Effort and Delay Discounting in a Foraging Environment

### 2019-05-06 Cost2/Cost2_prereg_remake.Rmd
re-writing the code for Cost2 to make it shorter. At 16.1.3 right now

subjList <- unique(dataAll$SubjID)
# # load cognitive effort group
# setwd('./data/Cost2_data/cog')
# temp = list.files(pattern="*.csv")
# cogDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load wait group
# setwd('../wait')
# temp = list.files(pattern="*.csv")
# waitDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load physical group
# setwd('../phys')
# temp = list.files(pattern="*.csv")
# physDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load pheasysical group
# setwd('../easy')
# temp = list.files(pattern="*.csv")
# easyDataLong = lapply(temp, read.csv, header = FALSE)

### cleaning data
# this will generate a simple list with only info about trials that participants quit or completed
# this is because cognitive logs also include within-trial task-specific information
# for the wait condition, it will get rid of the break indicator

nSubsW <- length(waitDataLong)
nSubsC <- length(cogDataLong)
nSubsP <- length(physDataLong)
nSubsE <- length(easyDataLong)
totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE)

#  short lists
cogData <- list()
waitData <- list()
physData <- list()
easyData <- list()

# For pre-post analysis
cogBefore <- list()
cogAfter <- list()
waitBefore <- list()
waitAfter <- list()
physBefore <- list()
physAfter <- list()
easyBefore <- list()
easyAfter <- list()

# clean wait group data
for (subject in seq(nSubsW)){

  # Before/after
  breakW <- which(waitDataLong[[subject]]$V1 == 0)

  waitBefore[[subject]] <- waitDataLong[[subject]][1:(breakW - 1),]
  waitAfter[[subject]] <- waitDataLong[[subject]][(breakW + 1):length(waitDataLong[[subject]]$V1),]

  # assign header names
  colnames(waitBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(waitAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # Overall data cleaning
  tempW <- waitDataLong[[subject]]$V1 != 0

  # create a new list with only decision trials / without break
  waitData[[subject]] <- waitDataLong[[subject]][tempW,]

  # assign header names
  colnames(waitData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

# clean cognitive group data
for (subject in seq(nSubsC)){

  # Before/After
  breakC <- which(cogDataLong[[subject]]$V1 == 0)

  cogBefore[[subject]] <- cogDataLong[[subject]][1:(breakC-1),]
  temp <- cogBefore[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))
  cogBefore[[subject]] <- cogBefore[[subject]][decisionTrials,]

  cogAfter[[subject]] <- cogDataLong[[subject]][(breakC+1):length(cogDataLong[[subject]]$V1),]
  temp <- cogAfter[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))
  cogAfter[[subject]] <- cogAfter[[subject]][decisionTrials,]

  colnames(cogBefore[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                      "Experiment Time","Trial Outcome","Task Type","Task Setup")
  colnames(cogAfter[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                     "Experiment Time","Trial Outcome","Task Type","Task Setup")

  # Overall data cleaning
  # create an index for the trials in which a decision was made (completed, quit) 
  temp <- cogDataLong[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))

  # create a new list with only decision trials / without break
  tempC <- cogDataLong[[subject]]$V1 != 0  
  cogData[[subject]] <- cogDataLong[[subject]][decisionTrials,]
  cogDataLong[[subject]] <- cogDataLong[[subject]][tempC,]

  colnames(cogData[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                    "Experiment Time","Trial Outcome","Task Type","Task Setup")
  colnames(cogDataLong[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                        "Experiment Time","Trial Outcome","Task Type","Task Setup") # Long contains within-trial info

# clean physical group data
for (subject in seq(nSubsP)){

  # Before/After
  breakP <- which(physDataLong[[subject]]$V1 == 0)

  physBefore[[subject]] <- physDataLong[[subject]][1:(breakP - 1),]
  physAfter[[subject]] <- physDataLong[[subject]][(breakP + 1):length(physDataLong[[subject]]$V1),]

  colnames(physBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(physAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # create a new list with only decision trials / without break  
  tempP <- physDataLong[[subject]]$V1 != 0
  physData[[subject]] <- physDataLong[[subject]][tempP,]
  colnames(physData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

# clean pheaysical group data
for (subject in seq(nSubsE)){

  # Before/After
  breakE <- which(easyDataLong[[subject]]$V1 == 0)

  easyBefore[[subject]] <- easyDataLong[[subject]][1:(breakE - 1),]
  easyAfter[[subject]] <- easyDataLong[[subject]][(breakE + 1):length(easyDataLong[[subject]]$V1),]

  colnames(easyBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(easyAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # create a new list with only decision trials / without break  
  tempE <- easyDataLong[[subject]]$V1 != 0
  easyData[[subject]] <- easyDataLong[[subject]][tempE,]
  colnames(easyData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

# Combine before/after across subjects
cBefore <- rbind(cogBefore[[1]],cogBefore[[2]]) 
cAfter <- rbind(cogAfter[[1]],cogAfter[[2]]) 
wBefore <- rbind(waitBefore[[1]],waitBefore[[2]]) 
wAfter <- rbind(waitAfter[[1]],waitAfter[[2]]) 
pBefore <- rbind(easyBefore[[1]],physBefore[[2]])
pAfter <- rbind(physAfter[[1]],physAfter[[2]])
eBefore <- rbind(easyBefore[[1]],easyBefore[[2]])
eAfter <- rbind(easyAfter[[1]],easyAfter[[2]])

for (i in 3:nSubsW){

    wBefore <- rbind(wBefore,waitBefore[[i]])
    wAfter <- rbind(wAfter,waitAfter[[i]])

for (i in 3:nSubsC){

    cBefore <- rbind(cBefore,cogBefore[[i]])  
    cAfter <- rbind(cAfter,cogAfter[[i]])

for (i in 3:nSubsP){

    pBefore <- rbind(pBefore,physBefore[[i]])
    pAfter <- rbind(pAfter,physAfter[[i]])

for (i in 3:nSubsE){

    eBefore <- rbind(eBefore,easyBefore[[i]])
    eAfter <- rbind(eAfter,easyAfter[[i]])

#rm(cogBefore,cogAfter,waitBefore,waitAfter)

# aggregate ADD PHYS
waitBeforeAll <- aggregate(wBefore$Choice,
          by = list(wBefore$Reward, wBefore$Handling),
          FUN = 'mean')
waitAfterAll <- aggregate(wAfter$Choice,
          by = list(wAfter$Reward, wAfter$Handling),
          FUN = 'mean')
cogBeforeAll <- aggregate(cBefore$Choice,
          by = list(cBefore$Reward, cBefore$Handling),
          FUN = 'mean')
cogAfterAll <- aggregate(cAfter$Choice,
          by = list(cAfter$Reward, cAfter$Handling),
          FUN = 'mean')
physBeforeAll <- aggregate(pBefore$Choice,
          by = list(pBefore$Reward, pBefore$Handling),
          FUN = 'mean')
physAfterAll <- aggregate(pAfter$Choice,
          by = list(pAfter$Reward, pAfter$Handling),
          FUN = 'mean')
easyBeforeAll <- aggregate(eBefore$Choice,
          by = list(eBefore$Reward, eBefore$Handling),
          FUN = 'mean')
easyAfterAll <- aggregate(eAfter$Choice,
          by = list(eAfter$Reward, eAfter$Handling),
          FUN = 'mean')

rm(cBefore,cAfter,wBefore,wAfter, pBefore, pAfter, eBefore, eAfter)

# remove unnecessary variables
rm(temp,tempW,tempC,quitTrials,completeTrials,decisionTrials,subject)
```

``` {r Basic Prepping, echo=FALSE}  
# params for reference
handling <- c(2, 10, 14)
cond <- c("Wait", "Cognitive", "Physical", "Easy")

# create data frame with summary stats
tempW <- summarizeData()
tempC <- summarizeData(Data = cogData, nSubs = nSubsC, type = "Cognitive")
tempP <- summarizeData(Data = physData, nSubs = nSubsP, type = "Physical")
tempE <- summarizeData(Data = easyData, nSubs = nSubsE, type = "Easy")

summaryData <- rbind(tempW,
                     tempC,
                     tempP,
                     tempE)

colnames(summaryData) <- c("Group", "propComplete", "Earnings", "RT", "forcedTravel")

summaryData$Cols <- c(rep(cols[1],nSubsW), rep(cols[2],nSubsC), rep(cols[3],nSubsP), rep(cols[4],nSubsE))
rm(tempW, tempC, tempP, tempE)

# Indexes for groups
indxWait <- seq(nSubsW)
indxWaitLong <- seq(nSubsW * 9) # 9 being the number of combinations
indxCog <- (nSubsW + 1):(nSubsW + nSubsC)
indxCogLong <- ((nSubsW * 9) + 1):((nSubsW * 9) + (nSubsC * 9))
indxPhys <- ((nSubsW + nSubsC) + 1):(nSubsW + nSubsC + nSubsP)
indxPhysLong <- ((nSubsW * 9) + (nSubsC * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9))
indxEasy <- ((nSubsW + nSubsC + nSubsP) + 1):totalSubs #(nSubsW + nSubsC + nSubsP + nSubsE)
indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))

# the other, just summarizing for all participants
# Not sure if this is necessary anymore
# allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
#                                 rep("Cognitive",nSubsC*3),
#                                 rep("Physical",nSubsP*3)),
#                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
#                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
#                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
#                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
#                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
#                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))

# Get the proportion completed per combination for GLMs
tempW <- propComplete()
tempC <- propComplete(Data = cogData, nSubs = nSubsC, indx = indxCog, type = "Cognitive")
tempP <- propComplete(Data = physData, nSubs = nSubsP, indx = indxPhys, type = "Physical")
tempE <- propComplete(Data = easyData, nSubs = nSubsE, indx = indxEasy, type = "Easy")

allProp2 <- rbind(tempW,
                  tempC,
                  tempP,
                  tempE)  
allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials

rm(tempW, tempC, tempP, tempE)

# add optimal vector and difference from optimal
wait <- c(rep(1,nSubsW*3),
          c(rep(0,nSubsW), rep(1,nSubsW*2)),
          c(rep(0,nSubsW*2), rep(1,nSubsW)))
cog <- c(rep(1,nSubsC*3),
          c(rep(0,nSubsC), rep(1,nSubsC*2)),
          c(rep(0,nSubsC*2), rep(1,nSubsC)))
phys <- c(rep(1,nSubsP*3),
          c(rep(0,nSubsP), rep(1,nSubsP*2)),
          c(rep(0,nSubsP*2), rep(1,nSubsP)))
easy <- c(rep(1,nSubsE*3),
          c(rep(0,nSubsE), rep(1,nSubsE*2)),
          c(rep(0,nSubsE*2), rep(1,nSubsE)))
allProp2$Optimal <- c(wait,cog,phys,easy)
allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete

# sort by subject ID
#allProp2 <- allProp2[order(allProp2$SubjID),]

# actual proportions and standard errors, and the optimal summary for plotting
trueProp <- aggregate(allProp2$propComplete,
            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
            FUN = 'mean')

trueSD <- aggregate(allProp2$propComplete,
          by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
          FUN = 'sd')
colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
trueProp$SE[1:9] <- (trueSD$x[1:9])/(sqrt(nSubsW))
trueProp$SE[10:18] <- (trueSD$x[10:18])/(sqrt(nSubsC))
trueProp$SE[19:27] <- (trueSD$x[19:27])/(sqrt(nSubsP))
trueProp$SE[28:36] <- (trueSD$x[28:36])/(sqrt(nSubsE))

trueProp$Optimal <- aggregate(allProp2$Optimal,
            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
            FUN = 'mean')$x
```

@@

``` {r 16.1.1., fig.align="center", fig.width=4, fig.height=4, echo=FALSE}
# Add an AR predictor based on the number of quits
waitData <- lapply(waitData, function(data) data %>% mutate(AR = seqQuits(Choice)))
cogData <- lapply(cogData, function(data) data %>% mutate(AR = seqQuits(Choice)))
physData <- lapply(physData, function(data) data %>% mutate(AR = seqQuits(Choice)))
easyData <- lapply(easyData, function(data) data %>% mutate(AR = seqQuits(Choice)))

# Logistic fits
waitLogis <- lapply(waitData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
cogLogis <- lapply(cogData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
physLogis <- lapply(physData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
easyLogis <- lapply(easyData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))

# Coefficients
waitLogis_coeffs <- t(sapply(waitLogis, "[[", "coefficients"))
cogLogis_coeffs <- t(sapply(cogLogis, "[[", "coefficients"))
physLogis_coeffs <- t(sapply(physLogis, "[[", "coefficients"))
easyLogis_coeffs <- t(sapply(easyLogis, "[[", "coefficients"))
allLogis_coeffs <- rbind(waitLogis_coeffs,
                         cogLogis_coeffs,
                         physLogis_coeffs,
                         easyLogis_coeffs)

# Rank sums
rankHand <- wilcox.test(allLogis_coeffs[,2])
rankReward <- wilcox.test(allLogis_coeffs[,3])

# Plot coeffs
temp <- melt(allLogis_coeffs[,2:3])
qplot(data = temp, x = Var2, y = value, geom = "boxplot") + 
  labs(title = "Handling and Reward Coefficients", x = "", y = "Coefficients") +
  geom_hline(yintercept = 0, alpha = 0.5) +
  theme_classic()

rm(waitLogis, cogLogis, physLogis, easyLogis)

@@

``` {r 16.1.2., echo=FALSE, fig.align="center"}
# Logistic fits
waitLogis <- lapply(waitData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
cogLogis <- lapply(cogData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
physLogis <- lapply(physData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
easyLogis <- lapply(easyData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))

# Coefficients
waitLogis_coeffs <- t(sapply(waitLogis, "[[", "coefficients"))
cogLogis_coeffs <- t(sapply(cogLogis, "[[", "coefficients"))
physLogis_coeffs <- t(sapply(physLogis, "[[", "coefficients"))
easyLogis_coeffs <- t(sapply(easyLogis, "[[", "coefficients"))
allLogis_coeffs <- rbind(waitLogis_coeffs,
                         cogLogis_coeffs,
                         physLogis_coeffs,
                         easyLogis_coeffs)

#waitLogis_coeffs <- sapply(waitLogis, function(data) (confint(data)[4,1] < 0 & confint(data)[4,2] > 0))

# Rank sums
rankAR <- wilcox.test(allLogis_coeffs[,4])

# Plot coeffs
temp <- melt(allLogis_coeffs[,2:4])

# The ugliest code, to check the existence of 0 on the CIs
AR_CIs <- data.frame(Subj = NULL, Low = NULL, High = NULL)
temp <- data.frame(Subj = seq(nSubsW), Low = rep(-0.1,nSubsW), High = rep(0,nSubsW))
for (i in seq(length(waitLogis))) {
  test <- tryCatch(round(confint(waitLogis[[i]]), digits = 2)[4,], error=function(e){})
  if(!is.null(test)) {
    temp$Low[i] <- test[1]
    temp$High[i] <- test[2]
  }
}
AR_CIs <- rbind(AR_CIs, temp)
temp <- data.frame(Subj = seq(nSubsC), Low = rep(0,nSubsC), High = rep(0,nSubsC))
for (i in seq(length(cogLogis))) {
  test <- tryCatch(round(confint(cogLogis[[i]]), digits = 2)[4,], error=function(e){})
  if(!is.null(test)) {
    temp$Low[i] <- test[1]
    temp$High[i] <- test[2]
  }
}
AR_CIs <- rbind(AR_CIs, temp)
temp <- data.frame(Subj = seq(nSubsP), Low = rep(0,nSubsP), High = rep(0,nSubsP))
for (i in seq(length(physLogis))) {
  test <- tryCatch(round(confint(physLogis[[i]]), digits = 2)[4,], error=function(e){})
  if(!is.null(test)) {
    temp$Low[i] <- test[1]
    temp$High[i] <- test[2]
  }
}
AR_CIs <- rbind(AR_CIs, temp)
temp <- data.frame(Subj = seq(nSubsE), Low = rep(0,nSubsE), High = rep(0,nSubsE))
for (i in seq(length(easyLogis))) {
  test <- tryCatch(round(confint(easyLogis[[i]]), digits = 2)[4,], error=function(e){})
  if(!is.null(test)) {
    temp$Low[i] <- test[1]
    temp$High[i] <- test[2]
  }
}
AR_CIs <- rbind(AR_CIs, temp)
AR_CIs$High[is.na(AR_CIs$High)] <- 0.1
AR_CIs$AR_Effect <- apply(AR_CIs,1, function(x) !(x[2] <= 0 & x[3] >= 0))

# Around 10% seemed to have been influenced by previous quitting
propAR_effects <- (sum(AR_CIs$AR_Effect) / totalSubs) * 100

rm(temp,waitLogis, cogLogis, physLogis, easyLogis)

>>>>

subjList <- unique(dataAll$SubjID)

``` {r Basic Prepping, echo=FALSE}  
# # params for reference
# handling <- c(2, 10, 14)
# cond <- c("Wait", "Cognitive", "Physical", "Easy")
# # create data frame with summary stats
# tempW <- summarizeData()
# tempC <- summarizeData(Data = cogData, nSubs = nSubsC, type = "Cognitive")
# tempP <- summarizeData(Data = physData, nSubs = nSubsP, type = "Physical")
# tempE <- summarizeData(Data = easyData, nSubs = nSubsE, type = "Easy")
# summaryData <- rbind(tempW,
#                      tempC,
#                      tempP,
#                      tempE)
# colnames(summaryData) <- c("Group", "propComplete", "Earnings", "RT", "forcedTravel")
# summaryData$Cols <- c(rep(cols[1],nSubsW), rep(cols[2],nSubsC), rep(cols[3],nSubsP), rep(cols[4],nSubsE))
# rm(tempW, tempC, tempP, tempE)
# # Indexes for groups
# indxWait <- seq(nSubsW)
# indxWaitLong <- seq(nSubsW * 9) # 9 being the number of combinations
# indxCog <- (nSubsW + 1):(nSubsW + nSubsC)
# indxCogLong <- ((nSubsW * 9) + 1):((nSubsW * 9) + (nSubsC * 9))
# indxPhys <- ((nSubsW + nSubsC) + 1):(nSubsW + nSubsC + nSubsP)
# indxPhysLong <- ((nSubsW * 9) + (nSubsC * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9))
# indxEasy <- ((nSubsW + nSubsC + nSubsP) + 1):totalSubs #(nSubsW + nSubsC + nSubsP + nSubsE)
# indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))
# # the other, just summarizing for all participants
# # Not sure if this is necessary anymore
# # allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
# #                                 rep("Cognitive",nSubsC*3),
# #                                 rep("Physical",nSubsP*3)),
# #                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
# #                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
# #                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
# #                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
# #                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
# #                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))
# # Get the proportion completed per combination for GLMs
# tempW <- propComplete()
# tempC <- propComplete(Data = cogData, nSubs = nSubsC, indx = indxCog, type = "Cognitive")
# tempP <- propComplete(Data = physData, nSubs = nSubsP, indx = indxPhys, type = "Physical")
# tempE <- propComplete(Data = easyData, nSubs = nSubsE, indx = indxEasy, type = "Easy")
# allProp2 <- rbind(tempW,
#                   tempC,
#                   tempP,
#                   tempE)  
# allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials
# rm(tempW, tempC, tempP, tempE)
# # add optimal vector and difference from optimal
# wait <- c(rep(1,nSubsW*3),
#           c(rep(0,nSubsW), rep(1,nSubsW*2)),
#           c(rep(0,nSubsW*2), rep(1,nSubsW)))
# cog <- c(rep(1,nSubsC*3),
#           c(rep(0,nSubsC), rep(1,nSubsC*2)),
#           c(rep(0,nSubsC*2), rep(1,nSubsC)))
# phys <- c(rep(1,nSubsP*3),
#           c(rep(0,nSubsP), rep(1,nSubsP*2)),
#           c(rep(0,nSubsP*2), rep(1,nSubsP)))
# easy <- c(rep(1,nSubsE*3),
#           c(rep(0,nSubsE), rep(1,nSubsE*2)),
#           c(rep(0,nSubsE*2), rep(1,nSubsE)))
# allProp2$Optimal <- c(wait,cog,phys,easy)
# allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete
# # sort by subject ID
# #allProp2 <- allProp2[order(allProp2$SubjID),]
# # actual proportions and standard errors, and the optimal summary for plotting
# trueProp <- aggregate(allProp2$propComplete,
#             by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
#             FUN = 'mean')
# trueSD <- aggregate(allProp2$propComplete,
#           by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
#           FUN = 'sd')
# colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
# trueProp$SE[1:9] <- (trueSD$x[1:9])/(sqrt(nSubsW))
# trueProp$SE[10:18] <- (trueSD$x[10:18])/(sqrt(nSubsC))
# trueProp$SE[19:27] <- (trueSD$x[19:27])/(sqrt(nSubsP))
# trueProp$SE[28:36] <- (trueSD$x[28:36])/(sqrt(nSubsE))
# trueProp$Optimal <- aggregate(allProp2$Optimal,
#             by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
#             FUN = 'mean')$x

@@

``` {r 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
# filterout errors and compute R + H logistic per subject, then get coefficients
logisRH <- dataAll %>%
  filter(Choice < 2) %>%
  plyr::dlply("SubjID", identity) %>%
  lapply(function(data) {glm(Choice ~ Handling + Reward, data = data, family = "binomial")}) %>%
  sapply(coefficients)

# Rank sum tests
rankHand <- wilcox.test(logisRH["Handling", ])
rankReward <- wilcox.test(logisRH["Reward", ])

# Plot coeffs
temp <- melt(logisRH[c("Handling", "Reward"), ])
qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
  labs(title = "Handling and Reward Coefficients", x = "", y = "Coefficients") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = c(0.9, 0.7),
       panel.grid.major = element_blank(), 
       panel.grid.minor = element_blank(), 
       panel.background = element_blank(), 
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))
```

@@

``` {r 16.1.2., echo = FALSE, include = FALSE}
# add an AR regressor to track recent quits
logisRHAR <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID) %>%
  mutate(AR = seqQuits(Choice)) %>%
  plyr::dlply("SubjID", identity) %>%
  lapply(function(data) {glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial")})

# Rank sums
rankAR <- logisRHAR %>% 
  sapply(coefficients) %>%
  wilcox.test(.["AR", ])

AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(confint(x)[4, ], error = function(e){c(0, 0)})}) %>%
  replace_na(0) %>%
  t() %>% 
  apply(1, function(x) !(x[1] <= 0 & x[2] >= 0))

# Around 10% seemed to have been influenced by previous quitting
propAR_effects <- mean(AR_CIs) * 100
```
